\chapter*{References}
\addcontentsline{toc}{chapter}{References}

\begin{thebibliography}{99}

\bibitem{Nguyen2013MFM}
Nguyen, N. V., Gilard, V., and Bingol, O. (2013). Multidisciplinary Unmanned Combat Air Vehicle system design using Multi-Fidelity Model. \textit{Aerospace Science and Technology}. doi:10.1016/j.ast.2012.12.010.

\bibitem{Raymer2018}
Raymer, D. P. (2018). \textit{Aircraft Design: A Conceptual Approach} (6th ed.). AIAA.

\bibitem{Torenbeek1982}
Torenbeek, E. (1982). \textit{Synthesis of Subsonic Airplane Design}. Delft University Press.

\bibitem{Sharpe2021AeroSandbox}
Sharpe, P. D. (2021). \textit{AeroSandbox: A Differentiable Framework for Aircraft Design Optimization}. Master's thesis, Massachusetts Institute of Technology.

\bibitem{Bowers2023PrandtlD}
Bowers, A. H., et al. (2023). Wake-Structure of the Prandtl-D. AIAA SciTech.

\bibitem{Lafifi2020}
Lafifi, M. M. (2020). XFLR5 Analysis of foils and wings operating at low Reynolds numbers.

\bibitem{Drela1989XFOIL}
Drela, M. (1989). XFOIL: An Analysis and Design System for Low Reynolds Number Airfoils. In \textit{Low Reynolds Number Aerodynamics} (Conference Proceedings).

\bibitem{Sharpe2024Graph}
Sharpe, P. D. (2024). \textit{Accelerating Practical Engineering Design Optimization with Computational Graph Transformations}. Ph.D. thesis, Massachusetts Institute of Technology.

\bibitem{Sharpe2025NeuralFoil}
Sharpe, P. D. (2025). NeuralFoil: A physics-informed machine learning model for airfoil aerodynamics. arXiv:2503.16323.

\bibitem{Zhang2025ANNGA}
Zhang, Y., et al. (2025). Aerodynamic Design Optimization for Flying Wing Gliders Based on the Combination of Artificial Neural Networks and Genetic Algorithms. \textit{Aerospace}.

\bibitem{Botero2025SUAVE}
Botero, E., et al. (2025). Current Capabilities and Challenges of NDARC and SUAVE for eVTOL Aircraft Design and Analysis. Stanford University.

\bibitem{Vegh2019NDARCSUAVE}
Vegh, J. M., Botero, E., and coauthors (2019). Comparison of NDARC and SUAVE for an eVTOL aircraft conceptual design: Kitty Hawk Cora. Stanford University (SUAVE).

\bibitem{Deperrois2009XFLR5}
Deperrois, A. (2009). \textit{Guidelines for XFLR5 v6.03}. XFLR5 documentation.

\bibitem{Yu2022ICAS}
Yu, A., et al. (2022). Comparing Potential Flow Solvers for Aerodynamic Characteristics Estimation of the T-Flex UAV. \textit{ICAS 2022}.

\bibitem{RosasCordova2024VSPAERO}
Rosas-Cordova, A., et al. (2024). Validation of VSPAERO for Basic Wing Simulation. \textit{RIMNI}.

\bibitem{Szabo2022TFlex}
Szabo, A., et al. (2022). Comparing Potential Flow Solvers for Aerodynamic Characteristics Estimation of the T-Flex UAV. ICAS.

\bibitem{DrelaYoungren1988}
Drela, M., and Youngren, H. (1988). \textit{AVL User Primer}. MIT AeroAstro.

\bibitem{TechScience2024VSPAERO}
TechScience. (2024). Validation of VSPAERO for Basic Wing Simulation. RIMNI.

\bibitem{DrelaMotorModel}
Drela, M. First-Order DC Electric Motor Model.

\bibitem{Tremblay2007Battery}
Tremblay, O., Dessaint, L.-A., and Dekkiche, A. (2007). A Generic Battery Model for the Dynamic Simulation of Hybrid Electric Vehicles. \textit{IEEE Vehicle Power and Propulsion Conference}. doi:10.1109/VPPC.2007.4544139.

\bibitem{IncroperaDeWitt}
Incropera, F. P., and DeWitt, D. P. \textit{Fundamentals of Heat and Mass Transfer}.

\bibitem{Roskam}
Roskam, J. \textit{Airplane Flight Dynamics and Automatic Flight Controls}.

\bibitem{StevensLewis}
Stevens, B. L., and Lewis, F. L. \textit{Aircraft Control and Simulation}.

\bibitem{TimoshenkoGere}
Timoshenko, S. P., and Gere, J. M. \textit{Theory of Elastic Stability}.

\bibitem{Batdorf1947}
Batdorf (1947). NACA TN-2661.

\bibitem{Kreisselmeier1979}
Kreisselmeier, G., and Steinhauser, R. (1979). Systematic control design by optimizing a vector performance index.

\bibitem{Lekhnitskii1968}
Lekhnitskii (1968). \textit{Anisotropic Plates}.

\bibitem{Whitney1987}
Whitney (1987). \textit{Structural Analysis of Laminated Anisotropic Plates}.

\bibitem{NASASP8007}
NASA SP-8007. Buckling of Thin-Walled Circular Cylinders.

\bibitem{Bruhn}
Bruhn, E. F. \textit{Analysis and Design of Flight Vehicle Structures}.

\bibitem{Wagner1931}
Wagner, H. (1931). Flat Sheet Metal Girders with Very Thin Webs. NACA TM 604-606.

\bibitem{VonKarman1932}
von Karman, T., Sechler, E. E., and Donnell, L. H. (1932). The Strength of Thin Plates in Compression.

\bibitem{Niu}
Niu, M. C. Y. \textit{Airframe Structural Design}.

\bibitem{Megson}
Megson, T. H. G. \textit{Aircraft Structures for Engineering Students}.

\bibitem{Kulfan2008CST}
Kulfan, B. M. (2008). Universal Parametric Geometry Representation Method. \textit{Journal of Aircraft}, 45(1), 142--158. doi:10.2514/1.29958.

\bibitem{Andersson2019CasADi}
Andersson, J. A. E., Gillis, J., Horn, G., Rawlings, J. B., and Diehl, M. (2019). CasADi: a software framework for nonlinear optimization and optimal control. \textit{Mathematical Programming Computation}.

\bibitem{Pratt2000STEP}
Pratt, M. J. (2000). Introduction to ISO 10303 (STEP). NIST.

\bibitem{Nagel2012CPACS}
Nagel, B., et al. (2012). Communication in Aircraft Design: Can we establish a common language? \textit{ICAS 2012}.

\bibitem{Berndt2009JSBSim}
Berndt, J. (2009). JSBSim: An Open Source Flight Dynamics Model in C++. \textit{AIAA Modeling and Simulation Technologies Conference}. doi:10.2514/6.2009-5699.

\end{thebibliography}
